# Reproducible Research: Peer Assessment 1
============================================

## Loading and preprocessing the data
Load data from CSV file and keep the raw data set as "data1". 

```{r}
read.csv("activity.csv") -> data1
summary(data1)
```

## What is mean total number of steps taken per day?
Calculate total number of steps taken each day, save it as "tot_day", and make a histogram plot.
```{r}
tapply(data1$steps, data1$date, sum, na.rm=T) -> tot_day
hist(tot_day,20)
```

Calculate and report the mean and median total number of steps taken per day
```{r}
mean_day <- mean(tot_day)
median_day <- median(tot_day)
```
For total number of steps taken per day, the mean value is `r mean_day` steps, the median value is `r median_day` steps.

## What is the average daily activity pattern?

Using "reshape2" library, melt the raw data, and then cast it to calculate the mean value for each interval.
```{r}
library(reshape2)
melt(data1, id=c("date", "interval"))-> data3
dcast(data3, interval~variable, mean, na.rm=T) -> mean_int
plot(mean_int, type='l')
mean_int$interval[which(mean_int$steps == max(mean_int$steps))] -> max_int
```
Among the intervals, interval `r max_int` contains the maximum number of steps.

## Imputing missing values

Calculate and report the total number of missing values in the dataset

```{r}
sum(is.na(data1$steps)) -> miss_count

```
totally have `r miss_count` missing value

Replace the NA's by the mean value of that 5 min interval. And save it in "data4"
```{r}
data4 <- data1
for (i in which(is.na(data1$steps))) {
    data4[i, ]$steps <- mean_int[mean_int$interval==data4[i,]$interval,]$steps
    }
```
Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day
```{r}
tapply(data4$steps, data4$date, sum, na.rm=T) -> tot_day_new
hist(tot_day_new,20)
mean_day_new <- mean(tot_day_new)
median_day_new <- median(tot_day_new)
```
So, for total steps taken per day, after imputing missing data with 5 min interval mean value, the mean value is `r mean_day_new` steps, the median value is `r median_day_new` steps. They are different from previous value.

According to my calculation results, it seems that imputing missiong data have influence on the mean value and median value calculation, it creates a bigger number...



## Are there differences in activity patterns between weekdays and weekends?
Create a new factor variable in the dataset with two levels C “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r}
WeekendOrNot <- character(length = length(data4$date))
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期一"] <- "weekday"
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期二"] <- "weekday"
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期三"] <- "weekday"
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期四"] <- "weekday"
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期五"] <- "weekday"
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期六"] <- "weekend"
WeekendOrNot[weekdays(as.Date(data4$date)) =="星期日"] <- "weekend"
WeekendOrNot <- factor(WeekendOrNot, levels=c("weekday", "weekend"))
data4 <- cbind(data4, WeekendOrNot)
```
Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis)

```{r}
melt(data4, id = c("interval", "WeekendOrNot", "date"))-> data5
dcast(data5, interval + WeekendOrNot ~ variable, mean) -> data6
library(lattice)
xyplot(steps ~ interval | factor(WeekendOrNot), data = data6, aspect = 1/2, type = "l")
```

